\documentclass[a4paper, 11pt]{article}
\usepackage{comment} % enables the use of multi-line comments (\ifx \fi) 
\usepackage{lipsum} %This package just generates Lorem Ipsum filler text. 
\usepackage{fullpage} % changes the margin
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}

\usepackage{booktabs}

\usepackage{sectsty}

\sectionfont{\fontsize{12}{15}\selectfont}

\begin{document}

	\begin{center}
		{\bf Proposal for Google Research Awards (PhD. level) - Latin America}
	\end{center}

	\section{Overview}

	\noindent
	{\bf Proposal Title:} \\
	{\bf Faculty Full Name:} Luiz Fernando Bittencourt \hfill bit@ic.unicamp.br \\
	{\bf PhD candidate:} Eduardo de Souza Gama \hfill eduardogama@lrc.ic.unicamp.br \\
	{\bf Google Contact name:} Walfredo Cirne
	% \normalsize ECE 100-003 \hfill Teammates: Student1, Student2 \\
	% TA: Adam Sumner \hfill Due Date: XX/XX/XX


	\section{Proposal Body}	
	
	\input{abstract}
	
    \input{research-goals}

    \input{contributions}
    
    \input{releated-work}

    \input{data-policy}

\begin{thebibliography}{9}

\bibitem{Bittencourt} Luiz F. Bittencourt, Márcio Moraes Lopes, Ioan Petri, Omer F. Rana \emph{Towards Virtual Machine Migration in Fog Computing}. 10th International Conference on P2P, Parallel, Grid, Cloud and Internet Computing. 2015.

\bibitem{BittencourtII} Luiz F. Bittencourt, Omer F. Rana, and Ioan Petri,. \emph{Cloud Computing at the Edges}. Springer International Publishing. 2016. pp. 3–12.

\bibitem{Byers}  Byers, Charles C. and Wetterwald, Patrick. 2015. \emph{Fog Computing Distributing Data and Intelligence for Resiliency and Scale Necessary for IoT: The Internet of Things (Ubiquity Symposium)}. Ubiquity 2015, November, Article 4 (November 2015), 12 pages.

\bibitem{Bonomi} F. Bonomi, R. Milito, J. Zhu, and S. Addepalli \emph{Fog computing and its role in the internet of things}. In workshop on Mobile cloud computing. ACM, 2012.

\bibitem{StojmenovicI} I. Stojmenovic \emph{Fog computing: A cloud to the ground support for smart things and machine-to-machine networks}. In ATNAC. IEEE, 2014.

\bibitem{StojmenovicII} I. Stojmenovic and S. Wen \emph{The fog computing paradigm: Scenarios and security issues}. In Computer Science and Information Systems (FedCSIS), 2014 Federated Conference on, 2014.

\bibitem{Evans}  D. Evans 2005. \emph{The Internet of Things: How the Next Evolution of the Internet Is Changing Everything}[online]. Disponível em: \url{http://www.cisco.com/c/dam/en_us/about/ac79/docs/innov/IoT_IBSG_0411FINAL.pdf}

\bibitem{Shanhe}  Shanhe Yi, Zhengrui Qin, and Qun Li. \emph{Security and Privacy Issues of Fog Computing: A Survey}. The 10th International Conference on Wireless Algorithms, Systems, and Applications (WASA), 2015.


% \bibitem{Jaydip} Jaydip Sen. \emph{Security and Privacy Issues in Cloud Computing}[online]. Disponível em: \url{https://arxiv.org/pdf/1303.4814.pdf}.


% \bibitem{Flueck}  Flueck, Alexander J. 2005. \emph{ECE 100}[online]. Chicago: Illinois Institute of Technology, Electrical and Computer Engineering Department, 2005 [cited 30 August 2005]. Available from World Wide Web: (http://www.ece.iit.edu/~flueck/ece100).

\end{thebibliography}
	
	\section{Attach CVs (maximum two pages for CVs)}
	


\end{document}